\huge A Usability Evaluation of Tor Launcher

### 2016-10-21 pets2017-paper/pets2017-paper.tex
write the testing pipeline subsection

\section{Methodology}

\subsection{Testing Procedure} 
{\color {blue}

Procedure: inspection, formative, design, summative.

We wanted to inspect the thing ourselves before doing formative testing so we know what to look for. 
We did a heuristic walkthrough, not a pluralistic walkthrough or cognitive walkthrough. 
%~\cite{nielsen1994usability} %inspection methods book
%http://www.usabilitybok.org/heuristic-walkthrough
%http://www.usabilitybok.org/pluralistic-walkthrough
%http://www.usabilitybok.org/cognitive-walkthrough

Formative usability testing is a support tool used during the beginning stages of the design process to provide insights of where users have difficulty. With formative user testing, it is enough to test 3–5 users. After the fifth user, you have all the insight you are likely to get and your best bet is to go back to the drawing board and improve the design so that you can test it again. Testing more than five users wastes resources, reducing the number of design iterations and compromising the final design quality.

%http://www.usabilitybok.org/Formative-evaluation
%https://www.nngroup.com/articles/why-you-only-need-to-test-with-5-users/ ~\cite{howmanyusers}

We wanted to try an anternative interface to see if we can make any improvements. We wanted to, since we had all this testing! But we can also test the original design in a formative and summative way.

Summative usability testing is a quality assurance test usually performed later in the development process. While formative tells you what isn't usable, while summative tells you if it is usable. This works on the assumption that the design direction is the right one and that there is potential for a usable solution, and thus the summative usability testing determines whether the execution actually delivers on that promise.
%http://www.usabilitybok.org/Summative-evaluation
%https://www.nngroup.com/articles/quantitative-studies-how-many-users/
%~\cite{summative}
}

>>>>

\section{Methodology} 
This section talks about our process, principles, and preparations for evaluating the configuration interface.

\subsection{Testing Pipeline} 
Two researchers first performed a cognitive walkthough~\cite{cognitive-walkthrough} to prepare for user testing. A cognitive walkthough is evaluation method in which usability evaluators and product experts work through a series of tasks from the perspective of the user to understand a system's learnability for new or infrequent users.

We then conducted a formative usability test~\cite{formative} that found where and why users have difficulty. Formative usability testing is a support tool designed to gain insight into how the design can be improved. 5 users is considered to be user testing's maximum benefit-cost ratio for gaining insights~\cite{howmanyusers}, so we recruited for 5 participants in each experimental condition.

Formative testing is usually used as feedback for design iterations. We opportunistically used our observations to make design changes to the configuration interface. We believed that the process of a identifying design principles, proposing design changes, and showing an alternative interface was insightful in itself---and had the potential to discover impactful changes.

We concluded with a summative usability test~\cite{summative} that determined the usability of an interface. We test the current interface to evaluate it and test the redesigned interface to see if our design changes had impact. Summative usability testing is a qualtiy assurance tool designed to test features in a design. In short, formative usability tells you what isn't usable, while summative usability testing tells you if it is usable. 20 users is considered to be the minimum number to statistically significant measurments~\cite{howmanyusers}, so we recruited for 20 participants in each experimental condition.
